Title here

### 2020-09-29 paper/paper.Rmd
shows a selected number of frames of the animated pca plot/ tour

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

@@

```{r toy-pca, fig.height = 6, fig.cap = "\\label{toy-pca}PCA plot of search geodesic colouring by info allows for better understanding of each stage in the geodesic search"}
path1 <- holes_1d_geo$basis %>% 
  flatten_dbl() %>% 
  matrix(ncol = 5, byrow = TRUE)
path2 <- holes_1d_better$basis %>% 
  flatten_dbl() %>% 
  matrix(ncol = 5, byrow = TRUE)
set.seed(1)
sphere <- geozoo::sphere.hollow(p = 5, n = 1000)$point
theoretical <- matrix(c(0, 1, 0, 0, 0,
                        0, -1, 0, 0, 0), nrow = 2, byrow = TRUE)

@@

```{r cache = TRUE, eval=FALSE}
# rl <- lapply(list.files(here::here("figures/animated_pca_1d/"),full.names = TRUE)[62:78], png::readPNG)
# gl <-  lapply(rl, grid::rasterGrob)
# gridExtra::grid.arrange(grobs=gl)
ani <- p +
  transition_states(id) +
  shadow_mark()

animate(ani, nframes = 350)
anim_save(ani, nframes = 350, filename = "figures/animated_pca_1d")
```

@@

```{r eval = FALSE}
set.seed(1)
sphere <- geozoo::sphere.hollow(p = 5, n = 1000)$point
path1 <- holes_1d_geo$basis %>% 
  flatten_dbl() %>% matrix(ncol = 5, byrow = TRUE)
path2 <- holes_1d_better$basis %>% 
  flatten_dbl() %>% matrix(ncol = 5, byrow = TRUE)
dt <- rbind(sphere, path1, path2)
colnames(dt) <- c(map_chr(1:5, ~paste0("x", .x)))
pal <- c("#1B9E77","#D95F02","#7570B3", "#E7298A")
color <- c(rep(pal[1], nrow(sphere)),
           rep(pal[2], nrow(path1)),
           rep(pal[3], nrow(path2)))
animate_xy(dt, col = color, cex_slice = 0.8)
animate_slice(dt, col = color)

@@

holes_2d_better %>% mutate(max_tries = 25) %>% 
  dplyr::bind_rows(holes_2d_better_max_tries %>% mutate(max_tries = 500)) %>% 
  explore_trace_interp(col = max_tries, facet = max_tries) + 
  theme(legend.position = "none")
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE,root.dir = here::here())

@@

```{r toy-pca, fig.height = 4, fig.cap = "\\label{toy-pca}PCA plot of search geodesic colouring by info allows for better understanding of each stage in the geodesic search"}
path1 <- holes_1d_geo$basis %>% 
  flatten_dbl() %>% 
  matrix(ncol = 5, byrow = TRUE)
path2 <- holes_1d_better$basis %>% 
  flatten_dbl() %>% 
  matrix(ncol = 5, byrow = TRUE)
set.seed(1)
sphere <- geozoo::sphere.hollow(p = 5, n = 1000)$point
theoretical <- matrix(c(0, 1, 0, 0, 0,
                        0, -1, 0, 0, 0), nrow = 2, byrow = TRUE)

@@

```{r fig.cap = "THis is the caption", fig.height=4, fig.align="center"}
# ani <- p + theme(legend.position = "none") +
#   transition_states(id) +
#   shadow_mark()
# 
# animate(ani, nframes = 350, device = "png",
#         renderer = file_renderer("figures/pca/",
#                                  prefix = "pca", overwrite = TRUE))

frames <- c("0002", "0058", "0078", "0117", "0172", "0350")
ani <- paste0(here::here("figures/"), "pca/", "pca", frames, ".png")
rl <- lapply(ani, png::readPNG)
gl <-  lapply(rl, grid::rasterGrob)
wrap_plots(gl) 
```

@@

```{r fig.cap="THis is te caption"}
set.seed(1)
sphere <- geozoo::sphere.hollow(p = 5, n = 1000)$point
path1 <- holes_1d_better$basis %>% 
  flatten_dbl() %>% matrix(ncol = 5, byrow = TRUE)
path2 <- holes_1d_geo$basis %>% 
  flatten_dbl() %>% matrix(ncol = 5, byrow = TRUE)
theoretical <- matrix(c(0, 1, 0, 0, 0,
                        0, -1, 0, 0, 0), nrow = 2, byrow = TRUE)
start <- get_start(holes_1d_better) %>% pull(basis) %>% .[[1]] %>% matrix(nrow = 1)
dt <- rbind(sphere, path1, path2, theoretical, start)
colnames(dt) <- c(map_chr(1:5, ~paste0("x", .x)))
pal <- c("#D3D3D3",c("#524340",  #orchre
                     "#B4B754",  # green
                     "#F3B422" # yellow
                     ))
color <- c(rep(pal[1], nrow(sphere)),
           rep(pal[2], nrow(path1)),
           rep(pal[3], nrow(path2)),
           rep(pal[4], 2), 
           pal[2] # for start
           )
cex <- c(rep(1, nrow(sphere)),
         rep(1.5, nrow(path1)), 
         rep(1.5, nrow(path2)), 
         rep(5, 2), 
         5 # for start
         )

#animate_xy(dt, col = color, cex = cex, tour_path = grand_tour()) # trial

# set.seed(123)
# render(
#   dt,
#   tour_path = grand_tour(),
#   dev = "png",
#   display = display_xy(col=color,cex = cex, axes = "bottomleft"),
#   rescale = FALSE,
#   frames = 500,
#   here::here("figures","tour", "tour%03d.png")
# )

frames <- c("001", "143", "078", "117", "172", "350")
ani <- paste0(here::here("figures/"), "tour/", "tour", frames, ".png")
rl <- lapply(ani, png::readPNG)
gl <-  lapply(rl, grid::rasterGrob)
wrap_plots(gl) 
```

@@

holes_2d_better %>% mutate(max_tries = 25) %>% 
  dplyr::bind_rows(holes_2d_better_max_tries %>% mutate(max_tries = 500)) %>% 
  explore_trace_interp(col = max_tries) + 
  theme(legend.position = "none")
```
